Sandbox Testing Latex

### 2019-06-25 _other/pandoc/fansampleBACKDOCX.tex
pandoc converted to doc from updated tex

is a paper on Human Capital.

@@

\hypertarget{convert-from-tex-to-word-and-markdown}{%
\subsection{Convert from tex to word and
markdown}\label{convert-from-tex-to-word-and-markdown}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{run this for tex to word}: pandoc -s fansample.tex -o
  fansample.docx
\item
  \emph{run this for tex to md}: pandoc -s fansample.tex -o fansample.md
\end{enumerate}

\hypertarget{convert-from-back-to-tex-from-word-and-markdown}{%
\subsection{Convert from back to tex from word and
markdown}\label{convert-from-back-to-tex-from-word-and-markdown}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  run this to convert tex to word: pandoc -s fansample.tex -o
  fansample.docx
\item
  run this to convert tex to markdown: pandoc -s fansample.tex -o
  fansample.md
\end{enumerate}

\hypertarget{convert-with-bibliography}{%
\subsection{Convert with Bibliography}\label{convert-with-bibliography}}

Suppose the file pandoc --bibliography=BiblatexChinaClosureWestern.bib
-o Draft20180210.docx Draft20180210.tex

>>>>

Becker and Tomes (1986) is a paper on Human Capital. Early childhood
health and economic circumstances could have lasting effects on adult
socioeconomic outcomes (Case, Fertig, and Paxson 2005).\footnote{"In
  this article, we develop a framework for analyzing the causal effects
  of interventions in the presence of latent factors that could affect
  outcomes, even in the absence of interventions" (Conti and Heckman
  2010).}

@@

\hypertarget{convert-from-tex-to-word-with-bibliography}{%
\subsection{Convert from Tex to Word with
bibliography}\label{convert-from-tex-to-word-with-bibliography}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{run this for word to tex}: pandoc --bibliography=fansample.bib
  -o fansample.docx fansample.tex
\end{enumerate}

\hypertarget{convert-from-word-from-tex}{%
\subsection{Convert from Word from
Tex}\label{convert-from-word-from-tex}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{run this for word to tex}: pandoc -s fansample.docx -o
  fansampleBACKDOCX.tex
\end{enumerate}

Becker, Gary S, and Nigel Tomes. 1986. ``Human Capital and the Rise and
Fall of Families.'' \emph{Journal of Labor Economics} 4 (3): S1--39.
\url{http://ideas.repec.org/a/ucp/jlabec/v4y1986i3ps1-39.html}.

Case, Anne, Angela Fertig, and Christina Paxson. 2005. ``The Lasting
Impact of Childhood Health and Circumstance.'' \emph{Journal of Health
Economics} 24 (2): 365--89.
\url{https://doi.org/10.1016/j.jhealeco.2004.09.008}.

Conti, Gabriella, and James J Heckman. 2010. ``Understanding the Early
Origins of the Education--Health Gradient.'' \emph{Perspectives on
Psychological Science} 5 (5): 585--605.
\url{https://doi.org/10.1177/1745691610383502}.
